---
title: "p8105_hw5_LF2649"
author: "Lin Feng"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document


---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(p8105.datasets)
knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis" 
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1

Read in data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled 
  n_total  
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```





## Problem 2

### Import and tidy the data
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

*Start with a dataframe containing all file names; the list.files function will help

*Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

*Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary


```{r}
readin = function (x){
  read_csv(x)
}

participants_df = 
  tibble(
    path = list.files("data"),
  ) %>% 
  mutate(
    path = str_c("./data/", path),
    data = map(path, readin)) %>% 
  unnest() %>% 
  separate(path, sep="/", into = c("1","2","path") ) %>% 
  select(3:week_8)%>% 
  separate(path, sep = ".csv", into = c("id", "csv")) %>% 
  separate(id, sep = "_", into = c("arm", "id")) %>% 
  select(id, arm, week_1:week_8)

ptcp_tidy =
  participants_df %>% 
  pivot_longer(
    "week_1":"week_8",
    names_to = "week",
    values_to = "values"
  )

```
### Spaghetti plot

*Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups

```{r}
spaghetti_plot = 
ptcp_tidy %>% 
  ggplot(aes(x = week, y = values, group = id)) + 
  geom_line() + 
  facet_grid(. ~ arm)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```


## Problem 3

### Generate 5000 datasets
```{r}
#Create a function to generate dataset

sample = function(n, mean, sd){
samp_data = tibble(
samp = rnorm(n, mean, sd)
)
samp_result = nest(samp_data) %>%
mutate(
t_test = map(.x = data, ~t.test(x = .x,mu=0, alternative = 'two.sided', paired = FALSE, conf.level = 0.95))
)
return(samp_result)
}

#Test the function
sample(30, 0, 5)



#Generate 5000 datasets
samp_5000 = 
  rerun(5000, sample(30, 0, 5)) %>% 
  bind_rows()
  
```


