---
title: "p8105_hw5_LF2649"
author: "Lin Feng"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document


---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(p8105.datasets)
knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis" 
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1

Read in data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled 
  n_total  
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```





## Problem 2

### Import and tidy the data
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

*Start with a dataframe containing all file names; the list.files function will help

*Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

*Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary


```{r}
readin = function (x){
  read_csv(x)
}

participants_df = 
  tibble(
    path = list.files("data"),
  ) %>% 
  mutate(
    path = str_c("./data/", path),
    data = map(path, readin)) %>% 
  unnest() %>% 
  separate(path, sep="/", into = c("1","2","path") ) %>% 
  select(3:week_8)%>% 
  separate(path, sep = ".csv", into = c("id", "csv")) %>% 
  separate(id, sep = "_", into = c("arm", "id")) %>% 
  select(id, arm, week_1:week_8)

ptcp_tidy =
  participants_df %>% 
  pivot_longer(
    "week_1":"week_8",
    names_to = "week",
    values_to = "values"
  )

```
### Spaghetti plot

*Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups

```{r}
spaghetti_plot = 
ptcp_tidy %>% 
  ggplot(aes(x = week, y = values, group = id)) + 
  geom_line() + 
  facet_grid(. ~ arm)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
```


## Problem 3

### Generate 5000 datasets

```{r}
sim_ttest = function(n, mu = 0, sigma = 5) {
 
  sim_data = tibble(
    x = rnorm(n = 30, mean = mu, sd = sigma),
  )
 
    ttest=t.test(sim_data, mu=0, sd=5)
    ttest[['p.value']]
    ttest[['estimate']]
   
  sim_results = tibble(
     pvalue = ttest[['p.value']],
     mean = ttest[['estimate']]
  )
}


output = vector("list", 5000)
for (i in 1:5000) {
  output[[i]] = sim_ttest(30)
}

sim_results = bind_rows(output)


#test
sim_results1 =
  rerun(5000, sim_ttest(30, 1, 5)) %>%
  bind_rows()
```


Simulating across multiple means.
```{r}

sim_results = 
  tibble(mn = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = mn, ~rerun(5000, sim_ttest(30, mu = .x, 5))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)



```

## Making plot

* Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

**Answer:**
As the mean increases we can find a trend that the power also increases. 

```{r}

plot_1 = 
sim_results %>% 
  mutate(
    reject = ifelse( pvalue < 0.05, 1, 0)) %>% 
  group_by(mn) %>% 
  mutate (
    proportion = mean(reject), 
        true_mean = str_c("mean=", mn)) %>% 
  slice(1) %>% 
  ggplot(aes(x = true_mean, y = proportion)) + 
  geom_point()



```


* Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. 

```{r}
plot_2 = 
sim_results %>% 
  group_by(mn) %>% 
  mutate (
    avg_mu_hat = mean(mean), 
    true_mean = mn) %>% 
  slice(1) %>% 
  ggplot(aes(x = true_mean, y = avg_mu_hat)) + 
  geom_point() 

```


* Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis.
* Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?



**Answer:**
The two plots are not the same. The reason could be that if we can reject the null when true_mean is small, we estimated the mean_hat will be greatly different from the true than when the true_mean is larger. 


```{r}
plot_3 = 
sim_results %>% 
  filter(pvalue < 0.05) %>% 
  group_by(mn) %>% 
  mutate (
    avg_mu_hat = mean(mean), 
    true_mean =  mn) %>% 
  slice(1) %>% 
  ggplot(aes(x = true_mean, y = avg_mu_hat)) + 
  geom_point()
  
  
plot_2 + plot_3
```

